---
title: "GAMLSS-Sandbox"
output: html_document
date: '2022-09-13'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(gamlss, gamlss.cens, gamlss.dist, gamlss.mx, gamlss.tr, ggplot2, tidyverse, ggpubr, skimr)
```

GAMLSS of control data from ENIGMA 22q against which to calculate cases' centiles (degree of abnormality from a given trajectory). Trajectories are calculated seperately for males and females across age.

## Cleaning

Questions:
- participants with repeat scans? (alfredo's script only keeps 1st instance)
- additional QC of results

```{r}
#load FreeSurfer Structural Data
fs.struc <- read.csv("/Users/megardn/Desktop/aab_rotation/_structural_stats.csv")

#summary(fs.struc)
#dim(fs.struc)
any(duplicated(fs.struc$subjId)) #check for duplicate subjects
n_unique(fs.struc$subjId)
fs.struc[duplicated(fs.struc$subjId),1] ### NEED TO CORRECT 09mm

#colnames(fs.struc)
#head(fs.struc)
```


```{r}
#calculate euler number
fs.struc <- fs.struc %>%
  mutate(euler = (2-2*SurfaceHoles))
summary(fs.struc$euler)
```


```{r}
#load demographics
demo <- read.csv("/Users/megardn/Desktop/aab_rotation/lifespan_data.csv")
colnames(demo) ### WHAT'S X?
dim(demo)

#drop structural data since we're getting that from FS spreadsheet
demo <- demo %>% select(1:4,11:19)
any(duplicated(demo$participant)) #check for duplicate subjects


demo.edit <- demo %>% mutate(participant = str_replace_all(participant, "_", ""), #removing _'s from participant IDs to match FS df
                             age_yrs=age_days/365.25) #calc age in yrs
```

Let's just try a simple join and see what happens

```{r}
#get distinct IDs between FS and demo subjects
no.fs <- left_join(demo.edit, fs.struc, by=c("participant"="subjId")) %>%
  filter(is.na(TotalGrayVol))

no.demo <- right_join(demo.edit, fs.struc, by=c("participant"="subjId")) %>%
  filter(is.na(sex))

#join
fs.demo <- left_join(demo.edit, fs.struc, by=c("participant"="subjId")) %>%
  drop_na(TotalGrayVol) 
dim(fs.demo) #proceeding with this df for now
```

## EDA


```{r}
#age frequency
fs.demo %>%
  ggplot(aes(age_yrs)) +
  geom_histogram(binwidth = 3, fill="darkgreen")

#holes
fs.demo %>%
  ggplot(aes(Holes)) +
  geom_histogram(binwidth = 5, fill="darkgreen")

#euler
fs.demo %>%
  ggplot(aes(euler)) +
  geom_histogram(binwidth = 5, fill="darkgreen")

#GM vs WM
ggplot(fs.demo, aes(x=TotalGrayVol, y=CerebralWhiteMatterVol)) +
  geom_point()
```

## GAMLSS

Pulls HEAVILY from Alfredo's `GAMLSS4CLIP_v1_R.r` for now

```{r}


```
