---
title: "GAMLSS Playground"
output: html_document
date: '2022-09-14'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(gamlss, gamlss.cens, gamlss.dist, gamlss.mx, gamlss.tr, ggplot2, tidyverse, ggpubr, skimr, gamlss.data)
```

Scripts for working through tutorials in Stasinopoulos's "Flexible Regression and Smoothing Using GAMLSS in R"

#### Intro/LMs

```{r lm}
head(rent)

r1 <- gamlss(R ~ Fl+A+H+loc, family=NO,  data=rent, trace=FALSE) #linear model
summary(r1)
```

family: defines distribution of response variable/link functions of parameters

`summary()` breakdown

Fitting method:

Mu link function:
Mu Coefficients:

Sigma Link function: type of function used to link sigma (SD) to data
-- log link -> sigma_hat=exp(Intercept Estimate)=exp(5.73165) to solve for standard deviation
Sigma Coefficients: plug into inverse link function to get SDs of parameter

Global Deviance: -2log(fitted likelihood of current fitted model)
AIC:
SBC: aka BIC
*GAIC:* generalized AIC, return using `GAIC(model, k)`
-- k=penalty parameter for each df

```{r}
#fitted(r1, "sigma") #maximum likelihood estimator of sigma (vector)
Rsq(r1) #R squared 
plot(r1) #plot residuals
```

Example violates non-homogeneity of variance, skewness assumptions

#### GLMs

about GLMs:
- response variable isn't assumed to be normally distributed ("exponential family of distributions")
- monotonic link function g() modes E(Y)'s relationship to explanatory variables
-- monotonic - function that preserves or reverses a given order (eg. if one variable changes with another, it won't mix that up)
- MLE for Beta parameters are calculated by iteratively reweighting least squares algorithm 

```{r glm}
r2 <-  gamlss(R ~ Fl+A+H+loc, family=GA,  data=rent)

#check AIC vs lm model
GAIC(r1, r2, k=0) #setting k=0 b/c both models have same # parameters (aka same df?)

plot(r2)
```

### GAM

Use smoother functions

taki 
hyperfine

```{r}


````




