---
title: "GAM+ Workshop Tutorial"
output: html_document
date: '2022-10-27'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Doing [workshop video on GAMs and GAMLSS](https://www.youtube.com/watch?v=a6sTwkQGt3E) from R Consortium, with accompanying exercises from [github](https://github.com/mfasiolo/workshop_UseR18).

### Workshop prep described in README:

```{r load_packages}
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(devtools, mgcViz)

install_github("mfasiolo/mgcFam")
install.packages(c("languageR", "gamair", "e1071"))
```

Test install:

```{r test, eval=FALSE}
set.seed(2) ## simulate some data...
dat <- gamSim(2,n=500,dist="normal",scale=0.25)$data
b <- qgamV(y ~ s(x, z), data = dat, qu = 0.5)
plotRGL(sm(b, 1), residuals = TRUE)

# Fit GAM and get gamViz object
b <- mqgamV(y~s(x) + s(z) + I(x*z), data = dat, qu = c(0.2, 0.4, 0.6, 0.8),
aQgam = list(argGam = list(select = TRUE)), aViz = list("nsim" = 0))
# Either way, we all effects by doing
print(plot(b, allTerms = TRUE), pages = 1)
```

## Intro  to GAMs

### Additive modeling
In GAM - distribution of y isn't necessarily gaussian but only mean is modeled as function of covariates
- additive b/c sum of functions of j covariates ($f_j(x)$, where $f_j$'s can be smooth, fixed, or random with coefficients $\beta$), transformed given a link function (g).
- smooth effects - second function you plug parameters into ($f_2$) which is a sum of "basis" (known) spline functions (B-splines) times a $\beta$ that scales them. This $\beta$ is unknown, so GAM estimates it to get best result when you combine all the shifted B-splines linearly
- Other Types of Smooths:
  - other options are cubic regression splines (basis function has a different shape) - minimmize sum of squares of y AND curvature parameter (goodness of fit whie balancing linearity, not too curvy/overfit)
  - also cyclic cubic regression splines (y at minimum x = y at maximum x)
  - adaptive smooth - penalize curvature of fit differently depending where you are on x axis (keep fit more or less strictly linear in different parts)
- thin plate regression splines - for multidimensional data, isotropic (one smoothing parameter/penalty for all dimensions of predictor data (ie x1, x2, etc))
    - works if x1 and x2 have the same units (otherwise use tensor product smooth)
- tensor product smooth - smooth in 1 dimension (z) then let teh spline vary smoothy by x dimension
  - x and z are penalized separately (eg cyclic smooth on one, cubic regression on another)
  - **can use almost any kind of marginal?? what's a marginal in this context?**
- by-factor smooth - smooth effect will vary by factor level
  - can do 2 different ways, with different smoothing parameters (penalty) by level and/or different random intercepts for each level
Fitting:
- chose rank r (number basis functions) that's big enough to be flexible BUT penalize regression coefficient $\beta$ to keep from overfitting (shrink towards 0)
- minimize penalized log likelihood (goodness of fit - complexity penalty)
Diagnostics:
- conditional residual checks - bin values, plot mean residual in each bin 
- effective degrees of freedom (EDF) - # parameters we're effectively using (k basis functions, but actually it's smaller b/c the penalty is shrinking things)
  - don't set too low, better to overestimate (default = 10)
  - see if your k is good by using conditional residuals check, increase k and see if model fit (AIC) improves, or `check(fit)` function:
    - if k' ~ edf -> might be smoothing too much
